Model Results

### 2018-02-16 paper/R/02_cleanAndCombine.Rmd
add sentiemtn analysis

## select politic section
```{r}
# pat1 <- "\\w\\.de/politik/deutschland"
# pat2 <- "\\w\\.de/politik/inland"
# pat3 <- "\\w\\.de/politik/wahl"
# pat4 <- "\\w\\.de/politik/bundestagswahl"
# pat5 <- "tagesschau.de/inland"
# 
# df %>%
#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
#                       sep="|"), url, perl = TRUE),1,0)) -> df

#........................
pat <- paste("cdu","csu","union","spd","fdp","afd",
             "linkspartei","die linke","die grünen","bündnis 90", sep="|")

df %>%
  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df
```

```{r}
btw <- df %>% filter(politics==1)
```

```{r}
btw %>%
  group_by(date, site) %>%
  dplyr::summarize(obs = n()) %>%
  ggplot(aes(date, obs, color = factor(site))) +
  geom_line() +
  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
  #           linetype = 2, color="grey40") +
  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
  #               linetype = 2, color="grey40") +
  #scale_color_manual(values = col) +
  labs(x="", y="Count",color="") +
  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))
```

@@

## Preparation
```{r}
btw <- btw %>% 
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
  filter(!grepl("sturm", url) |
           site != "Tagesschau.de") %>%
  filter(!grepl("Deutsche Bahn", text) | 
           site!="Tagesschau.de") %>%
  filter(!grepl("bahnstrecke", text) | 
           site!="Tagesschau.de")
```

>>>>

## select politic section
```{r}
pat1 <- "\\w\\.de/politik/deutschland"
pat2 <- "\\w\\.de/politik/inland"
pat3 <- "\\w\\.de/politik/wahl"
pat4 <- "\\w\\.de/politik/bundestagswahl"
pat5 <- "tagesschau.de/inland"

df %>%
  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
                      sep="|"), url, perl = TRUE),1,0)) -> df

#........................
# pat <- paste("cdu","csu","union","spd","fdp","afd",
#              "linkspartei","die linke","die grünen","bündnis 90", sep="|")
# 
# df %>%
#   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df

btw <- df %>% filter(politics==1)
```

@@

## Preparation

### 2018-02-16 paper/R/04_Modelresults.Rmd
add sentiemtn analysis

## Label topics
```{r}
sagelabs <- sageLabels(stmOut, 25)
```

@@

## 3.5 Plotquote
Take a closer look to those topics that are discussed most different.

```{r fig.height=6}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[23,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[23,], collapse="\n")))
```

>>>>

## Label topics
```{r}
sagelabs <- sageLabels(stmOut, 20)
```

@@

## Sentiment analysis

```{r}
sent <- c(
  # positive Wörter
  readLines("dict/SentiWS_v1.8c_Negative.txt",
            encoding = "UTF-8"),
  # negative Wörter
  readLines("dict/SentiWS_v1.8c_Positive.txt",
            encoding = "UTF-8")
) %>% lapply(function(x) {
  # Extrahieren der einzelnen Spalten
  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
  return(data.frame(words = res[1], value = res[2],
                    stringsAsFactors = FALSE))
}) %>%
  bind_rows %>% 
  mutate(word = gsub("\\|.*", "", words) %>% tolower,
         value = as.numeric(value)) %>% 
  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
```

Apply the dictionary on the artciles

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  unnest_tokens(word, text)

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(sentiment = as.numeric(value)) %>% 
  filter(!is.na(sentiment)) 
```

Calculate the number of total articles to weight the senitiment value.

```{r}
sentDF.red <- sentDF %>%

  # Count number of articles by medium
  group_by(site) %>% 
  add_tally() %>%
  ungroup() %>%
  mutate(totalcount = n) %>%
  select(-n) %>%

  # count number of articles by medium and topic
  group_by(site, topic_name) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(count = n) %>%
  mutate(weight = count/totalcount) %>%

  # calculate weight and weighted sentiment score
  group_by(site, topic_name) %>%
  summarize(sent_value = mean(sentiment),
            weight = mean(weight)) %>%
  mutate(weighted = sent_value*weight)
```

### Plot Sentiment

Unweighted
```{r fig.height=12}
sentDF.red %>%
  ggplot(aes(topic_name, sent_value)) +
  geom_col(fill=col[3], alpha=0.8) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="sentiment value") +
  theme(axis.text.x = element_text(size=10, angle = 90))

ggsave(filename = "../figs/sentiment.png", device = "png",width = 12, height = 8,
dpi = 600)
```

weighted
```{r fig.height=12}
sentDF.red %>%
  ggplot(aes(topic_name, weighted)) +
  geom_col(fill=col[3], alpha=0.8) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="sentiment value") +
  theme(axis.text.x = element_text(size=10, angle = 90))

ggsave(filename = "../figs/sent_weighted.png", device = "png",width = 12, height = 8,
dpi = 600)
```

### Radar plot
```{r}
library(radarchart)
```

```{r}
sentDF.red %>% 
  select(site, topic_name, sent_value) %>%
  spread(key=site, value=sent_value) %>%
  ungroup() -> radar
```

```{r}
chartJSRadar(scores = radar, labelSize = 8, 
             scaleStartValue = -0.15,
             maxScale = 0, 
             showToolTipLabel = TRUE,
             width = 8, height = 8)
```
